---
title: "BA810 individual assignment"
author: "Yuhong Lu (U68065591)"
date: "10/2/2019"
output: 
  pdf_document: default
---

# Setup
```{r}
library(tidyverse)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(glmnet)
theme_set(theme_bw())
```

# Load housing dataset
```{r}
house <- read_csv('housing.csv')

# replace na value in total_bedrooms col
total_bedrooms_median <- median(house$total_bedrooms, na.rm = T)
house <- house %>% replace_na(list("total_bedrooms" = total_bedrooms_median))
```

# Split into training and testing
```{r}
train_offsets <- seq(5000)
test_offsets <- 15000 + seq(3000)

x_data <- model.matrix( ~ -1 + total_rooms + total_bedrooms + households + housing_median_age + population + median_income + ocean_proximity, house)
y_data <- house$median_house_value / 1e6

x_train <- x_data[train_offsets, ]
y_train <- y_data[train_offsets]
x_test <- x_data[test_offsets, ]
y_test <- y_data[test_offsets]
```

# Run Lasso regressions
```{r}
est <- glmnet(x_train, y_train, alpha = 1, nlambda = 100)
est$lambda
length(est$lambda)
```

# Prediction
```{r}
y_train_hat <- predict(est, x_train)
y_test_hat <- predict(est, x_test)
dim(y_train_hat)
dim(y_test_hat)
```

# Compute MSEs
```{r}
mse_train <- vector()
for(i in 1 : ncol(y_train_hat)) {
  mse_train[i] <- mean((y_train_hat[,i] - y_train) ^ 2)
}

mse_test <- vector()
for(i in 1 : ncol(y_test_hat)) {
  mse_test[i] <- mean((y_test_hat[,i] - y_test) ^ 2)
}
```

# Aggregate all MSEs in a single dataset
```{r}
# Training MSEs
house_mse_train <- tibble(
  lambda = est$lambda,
  mse = mse_train,
  dataset = 'Train'
)
# Testing MSEs
house_mse_test <- tibble(
  lambda = est$lambda,
  mse = mse_test,
  dataset = 'Test'
)

house_mse <- rbind(house_mse_train, house_mse_test)
```

# Plot MSEs
```{r}
mse_min <- house_mse %>% 
  group_by(dataset) %>% 
  filter(mse == min(mse))

ggplot(house_mse, aes(lambda, mse, col = dataset)) +
  geom_line() +
  geom_point(data = mse_min, aes(lambda, mse)) +
  scale_x_reverse()
```

# Best fitting model
```{r}
# Lamda minimizes test MSE
lambda_min_mse_test <- mse_min$lambda[which(mse_min$dataset == 'Test')]
print(lambda_min_mse_test)

# Coefficient
coef(est, s = lambda_min_mse_test)
```
If I am a CA real estate investor, I will focus on housing age and hosing income as this two factors have the highest positive influence on the housing price. Then I will pay my attention to the population as it has the highest negative influence on the housing price. The other thing I will take my consideration is the location of the houses, houses on islands may have higher price while house inland may have negative influence on their price.

# Collaboration statement
I did the assignment by my own. Finished on Oct 3th, open source on my Github: https://github.com/yuhonglu-bu/BA810-Assignment.git.
